From the function-sheaf dictionary to quasicharacters of $p$-adic tori

### 2015-06-04 dictionary.tex
Added some justification for Weil sheaves. Still under construction, though.

@@

\subsection{Morphisms of characters} \label{ssec:CSmor}

>>>>

Let $G$ be the etale group scheme $\ZZ$ over $\Fq$ and consider the character $\chi : \ZZ \to \EEx$ of $G(\Fq)$ determined by $\chi(1) = 1+\ell$.
The stalk of $\cs{L}$ at the component $1$ is defined
by a pro-\'etale cover  . . .

@@

\subsection{On the necessity of working with Weil sheaves}

\begin{corollary} \label{cor:bounded}
Let $G$ be a smooth commutative group scheme over $\Fq$. 
Then $\cs{L}\in \CS(G)$ descends to $G$ if and only if $\trFrob{\cs{L}} : G(\Fq) \to \EEx$ has bounded image.
\end{corollary}
\begin{proof} 
By Lemma~\ref{lem:G0alg-grp}, the identity component $G^0$ is a connected algebraic group over $\Fq$. 
It follows from Proposition~\ref{prop:connected} that the restriction of $\cs{L}$ to $G^0$ descends to $G$. 
Also, since $G^0(\Fq)$ is finite, the image of $\trFrob{\cs{L}} : G(\Fq) \to \EEx$ is a finite subgroup and therefore bounded image.  
%
If $\chi \in G(\Fq)^*$ then there is some finite-image character $\chi_0$
with the same restriction to $G^0(\Fq)$ since $G^0(\Fq)$ is lies inside the torsion part of
the finitely generated abelian group $G(\Fq)$.  Therefore $\chi$ is bounded 
if and only if $\chi \cdot \chi_0^{-1}$ is bounded.  But $\chi \cdot \chi_0^{-1}$ descends
to a character of $\pi_0(G)$.
Thus, it is enough to prove Corollary~\ref{cor:bounded}
for \'etale group schemes $G$.

Now suppose $G$ is an etale group scheme over $\Fq$.
Let $\cs{L}$ be a character sheaf on $G$.
$[\alpha \oplus \beta \oplus 0]\in H^2(E)$.
 $b : \bG \to \EEx$ be a function

  By \cite{beilinson-bernstein-deligne:81a}*{Rem. 5.2.1},
$\cs{L}$ descends to $G$ if and only if $b(x) \in \EEx$ is bounded, for all $x$.

 . . . 
\end{proof}

Corollary~\ref{cor:bounded} shows that the full subcategory
$\bCS(G) \subset \CS(G)$ is not an equivalence, for smooth commutative group schemes $G$.
This simple observation reveals the necessity of working with Weil sheaves in Definition~\ref{def:CS}: one cannot geometrize all characters of $G(\Fq)$ using local systems on $G$, for general smooth commutative groups schemes $G$. 
For example, consider the case when $G$ is the discrete \'etale group scheme $\ZZ$.
If $\chi : \ZZ \to \EEx$ is the character of $G(\Fq)$ determined by $\chi(1) = \ell$
and if $\cs{L}$ is a character sheaf on $G$ in the isomorphism class
corresponding to $\chi$ under Theorem~\ref{thm:main},
then $\cs{L}$ does not descend to $G$ since the image of $\chi$ is not
bounded.

\subsection{Morphisms of character sheaves} \label{ssec:CSmor}
